\chapter*{Publications}
\addcontentsline{toc}{chapter}{Publications}

\section*{International conferences and workshops}
\begin{enumerate}
    \item Mazoyer, B., Cagé, J., Hervé, N. \& Hudelot, C. (2020). “A French Corpus for Event Detection on Twitter”. In “International Conference on Language Resources and Evaluation (LREC 2020)”, 6220–6227
    
    \item Evrard, M., Uro, R., Hervé, N. \& Mazoyer, B. (2020). “French Tweet Corpus for Automatic Stance Detection”. In “International Conference on Language Resources and Evaluation (LREC 2020)”, 6317–6322
    
    \item Mazoyer, B., Cagé, J., Hudelot, C., \& Viaud, M.-L. (2018). “Real-Time Collection of Reliable and Representative Tweets Datasets Related to News Events”. In “Proceedings of the First International Workshop on Analysis of Broad Dynamic Topics over Social Media (BroDyn 2018) co-located with the 40th European Conference on Information Retrieval (ECIR 2018)”, 23–34
\end{enumerate}

\section*{National conferences and workshops}
\begin{enumerate}
    \item Mazoyer, B., Hervé, N., Hudelot, C., \& Cagé, J. (2020). “Représentations lexicales pour la détection non supervisée d’événements dans un flux de tweets : étude sur des corpus français et anglais”. In “Extraction et Gestion des Connaissances (EGC 2020)”
    
    \item Mazoyer, B., Turenne, N., \& Viaud, M.-L. (2017). “Étude des influences réciproques entre médias sociaux et médias traditionnels”. In “Amsaleg, L., Claveau, V. \& Tannier, X. Actes de l’atelier Journalisme Computationnel 2017”, 37–40
\end{enumerate}

\section*{In preparation}
\begin{enumerate}
    \item Mazoyer, B., Hervé, N., Hudelot, C., \& Cagé, J. (2020). ``Short-Text Embeddings for Unsupervised Event Detection in a Stream of Tweets". \textit{In} ``Advances in Knowledge Discovery and Management", Vol 10 
    
    \item Mazoyer, B., Cagé, J., \& Hervé, N. (2020). ``Social Media and Newsroom Production Decisions"\\
\end{enumerate}